Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-16 lloveras_2020.tex
Mergeo de Diego + comentarios albert + cosas de fede + energi a de ceci, cosas varias.

\title{Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling\\
      \notebyalbert{\small Corregí filiación UNTREF, agregué segunda filiación para Fede (creo que no es preciso poner CBC, Fede?). Diego, ORCID IDs faltantes sacalos de {\tt orcid.org}}}

@@

\author[addressref={aff4},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}~\lnm{Sachdeva}\orcid{1}}

\author[addressref={aff4},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}~\lnm{Manchester IV}\orcid{2}}

\author[addressref={aff4},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}~\lnm{Van der Holst}\orcid{3}}

@@

\begin{abstract}
Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data \albert{for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, \albert{key to improve} their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24. Tomographic reconstructions and results of the model are analyzed in distinct coronal magnetic structures. We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it. We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the \albert{current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.

@@

For each open field line, and for each leg of the closed ones, an exponential fit was then applied to \albert{the $\sqravgN(r)$ data points, and a linear fit applied to the $\Tm(r)$ data points}, as described by

\albert{
\begin{eqnarray}\label{Nfit}
\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
\label{Tfit}
\Tm &=& T_0\,+\,m\,h
\end{eqnarray}
\noindent
where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere. In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop. In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop. The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.}

@@

To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}). The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $0.04\,10^8 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.

@@

To be selected a loop must meet all following conditions.

@@

\item 
Each leg of the loop must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the loop.

@@

For the two targeted rotations, DEMT and AWSoM resuls were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them. To that end four different types of legs corresponding with four different types of magnetic structures where selected:
%\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\

@@

\subsection{\albert{Energy input flux}}\label{energia}

@@

@@

Once the LDEM was determined for each rotation, the electron density $\Ne$ and electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}. As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} shows the latitude-longitude maps for both tomographic results for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$. Black voxels correspond to non-reconstructed voxels (explained in Section \ref{demt}). Thick-black curves indicate the open/closed boundaries based on the AWSoM model.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT \albert{products $\sqravgN$} (left panels) and $\Tm$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively. Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

@@

For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected. For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.

@@

As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the loop) \albert{electron temperature} $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $ \Ne(r=1.025\,\mrsun)$ as in previous articles. In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,065\,\mrsun$.

@@

\albert{En las discusiones usás type 1, 2 y 3, pero son I, II y III.} As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down loops in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. The amount of down loops in the equatorial latitudes. A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In blue the type 1 lines, populating all the streamer but mostly the mid latitudes. In red the type 2 lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type 3 lines, populating the coronal holes.

Of the 45000 legs selected in 2082, 14\% are type 0, 38\% are type 1, 23\% are type 3 and 25\% type 4, on the other hand of the 59000 legs selected in 2208, 8\% are type 0, 43\% are type 1, 22\% are type 3 and 30\% type 4.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of \albert{loops of type 0 (cyan), I (blue), II (red) and III (green)} at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel). See Section \ref{trace} for a definition of the different types of \albert{loops}. \notebyalbert{(by ALBERT) The population of DOWN loops in CR-2008 is negligible. These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.}  \notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors. I suggest these changes: cyan$\rightarrow$blue, blue$\rightarrow$red, red$\rightarrow$violet. In this way, blue will be DOWN loops and red will be UP loops, as in previous papers. The same change applies to Figure 4. Also, how about making Figures 3 and 4 a single Figure of four panels? Just an idea.} }
\label{rpoint_demt}
\end{center}
\end{figure}

To compare the results obtained with the traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$) for every type of line and for both rotations. The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values, according to DEMT results.

Both rotations are characterized by lines of type 0 with mean values of $-2.5\, \rm MK/\mrsun$, mean values of $2.3\, \rm MK/\mrsun$ in type 1 and $2.4\, \rm MK/\mrsun$ in type 2. The only notable difference is the smaller number of type 0 lines in CR-2208 and the mean value of $4.5\, \rm MK/\mrsun$ in type 3 for CR-2208 which is twice that for the other rotation.

\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Frequency histograms of the temperature radial gradient for the different \albert{four types of loops} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

\temp{este inicio de linea se repite del anterior}\\
As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines types. From top to bottom type 0 to type 4. From left to right the panels show the statistical distribution of \albert{$\NCB\equiv\sqravgN(r=1.055\,\mrsun)$}, $\lN$, $\aTm$, in each panel the median $m$ is indicated.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{\albert{Statistical distribution of DEMT results traced along loops of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} \notebyalbert{The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading. Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.}}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\diego{si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
From the equatorial streamer of both rotations, increasing latitudes show decreasing \temp{coronal base (1.055)} density, and increasing density scale height and electron temperature. In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of the equatorial streamer. Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres. \diego{no se si decir sharp queda bien.}

A comparison of the results between the two rotations shows that CR-2208 is characterized by lower values (between $11\%\, \rm and\, 16\%$) of electron density than CR-2082, higher values of density scale height (between $4\%\, \rm and\,19\%$) and higher values of electron temperature (between $6\%\, \rm and\,21\%$).

%To establish if the differences in the results between the two rotations are significant, Section \ref{uncertainties} estimates the error bars due the dominating systematic uncertainties.
\diego{Vale la pena introducir alguna comparacion sobre el campo magnetico????}
%{Also, within the streamer belt the magnetic field strength is similar in both rotations in the northern hemisphere, while in the southern hemisphere CR-1915 exhibits $10-80\%$ larger values compared to CR-2081, with increasing difference for larger latitudes. In the coronal holes, the magnetic field strength of CR-1915 is much larger than for CR-2081, exhibiting values up to 50\% larger in the northern hemisphere and more than twice larger in the southern hemisphere.}

\diego{Aca vienen quizas 1 o 2 parrafos  explicando los resultados de la Figura \ref{energia_demt}. Este parrafo va escrito por Ceci.}

>>>>

\title{Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling}

@@

\author[addressref={aff4},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}~\lnm{Sachdeva}\orcid{0000-0001-9114-6133}}

\author[addressref={aff4},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}~\lnm{Manchester IV}\orcid{0000-0003-0472-9408}}

\author[addressref={aff4},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}~\lnm{Van der Holst}\orcid{0000-0001-5260-3944}}

@@

\begin{abstract}
Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24. Tomographic reconstructions and results of the model are analyzed in distinct coronal magnetic structures. We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it. We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.

@@

For each open field line, and for each leg of the closed ones, an exponential fit was then applied to {the $\sqravgN(r)$ data points, and a linear fit applied to the $\Tm(r)$ data points}, as described by

\begin{eqnarray}\label{Nfit}
\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
\label{Tfit}
\Tm &=& T_0\,+\,m\,h
\end{eqnarray}
\noindent
where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere. In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop. In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop. The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.

@@

To measure how good the quality of the exponential fit to the electron density and the linear fit to the temperature data are, a chi-square merit function was used (see Section 15.2 \citet{recipes}). The errors were estimated in \citet{lloveras_2017}, $0.07$ MK for $\Tm$ and $4.0\,10^6 cm^{-3}$ for $\Ne$ and legs with p-value $>0.005$ were rejected.

@@

{To be selected a leg must meet all following conditions.}

@@

\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg.

@@

For the two targeted rotations, DEMT and AWSoM results were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them. To that end four different types of {legs} corresponding with four different types of magnetic structures were selected:
%\temp{Hacer explicacion de los tipos de lineas bien secos, luego en fig 3 hacer notar que implica cada una en cuanto a estructura magnetica}\\

@@

\subsection{{Energy input flux}}\label{energia}

@@

Due the difference between temperatures of transition region and solar corona, there must to be a heating mechanism that compensate all the losses present in the atmosphere and maintain stable the plasma temperature. Previous works have studied this mechanism by observations and modeling, but mostly for active regions. \citet{maccormack_2017} have developed a technique that estimate the heating injected into the loops during a period of minima activity. Using DEMT combined with an extrapolation of magnetic field, as we detailed before, they obtain the different plasma parameters along each magnetic loop, and therefore, compute the energy input flux required to maintain them stable.
The model assume a simple energy balance for each magnetic flux tube, where the losses by radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated by some coronal heating power($E_h$) \citep{aschwanden_2004}:

\begin{equation}\label{Balance}
E_h(s) = E_r(s)+ E_c(s),
\end{equation}

\noindent
where $s$ is the position along each magnetic flux tube and the powers are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.

Thermal conduction power is calculated by the Spitzer model \citep{spitzer_1962}, which describes coronal plasma regime properly. The thermal conduction power is obtained by taking the divergence of the conductive loss function $F_c(s)=-\kappa_0\,{T(s)}^{5/2}\,\frac{dT}{ds}(s)$, where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity. Due in coronal regime, the plasma is confined to the magnetic field, thus conduction is also predominately in the magnetic field direction. Thus, divergence is only the derivative along the position $s$:

\begin{equation}\label{Ec}
E_c(s)=\frac{1}{A(s)}\,\frac{d}{ds}\left[A(s)\,F_c(s)\right].
\end{equation}

\noindent
where $A(s)$ represent the magnetic flux tube area along the position $s$.

Radiative power depends on the amount of plasma in certain temperatures that can radiate. The model estimate it by integrating the squared density multiplied by a radiative loss function $\Lambda(T)$. This function depends on plasma temperature and is calculated by the atomic database and the plasma emission model from CHIANTI \citep{delzanna_2015}. Then, the expression for radiative power obtained is:

\begin{equation}\label{Er}
E_r = \int\,\Lambda(T)\,dN_e^2(T).
\end{equation}

Taking into acount the null divergence condition of magnetic field, the model integrate, between tomographic limits, each power quantities over magnetic flux tube independently of its area. Therefore, a loop-integrated equation for the energy flux balance is obtained ($[\rm{erg\,sec^{-1}\,cm^{-2}}]$):

\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c.
\end{equation}

\noindent
where $\phi_{h,r,c}$ are the loop-integrated energy input flux, radiative flux and conductive flux for each magnetic field line at 1.025 $R_{\odot}$.

For a complete description of the energy balance model, the reader can refer to \citet{maccormack_2017}.
We compute the loop-integrated energy quantities for both rotation analyzed in this work. 
\\

@@

{To perform a comparative study of the thermodynamic structure of the inner corona in different solar cycles
we carry out a DEMT reconstruction for two rotations: CR-2082, using STEREO/EUVI data and CR-2208, using SDO/AIA data.} {Once the LDEM was determined for each rotation, the square root of the mean value of the electron density squared $\sqravgN$ and the electron mean temperature $\Tm$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}.} As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the latitude-longitude maps of DEMT results for both rotations at {three different heights of interest. The lowest height where the tomography gives results, the lowest height where the AWSoM model results are reliable and a representative average height were selected, that is $r=$1.025, 1.065 and 1.105, $\mrsun$ respectively}. Black voxels correspond to non-reconstructed voxels (explained in Section \ref{demt}). Thick-black curve indicates the magnetic open/closed boundary based on the magnetic field of AWSoM model.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT {products $\sqravgN$} (left panels) and $\Tm$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively. Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

@@

{To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected. For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.

@@

As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr \Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data as a function of height may be used to compute the tomographic basal electron density at $\sqravgN(r=1.025\,\mrsun)$ as in previous articles. In this case, for further comparison analysis with the AWSoM results, we selected the lowest height where the results of the MHD model are reliable, that is $1,055\,\mrsun$.

@@

As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down {loops} in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In blue the type 1 lines, populating all the streamer but mostly the mid latitudes. In red the type 2 lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type 3 lines, populating the coronal holes.

Of the 45000 legs selected in 2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III, on the other hand of the 59000 legs selected in 2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of type 0 (cyan), I (blue), II (red) and III (green) at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel). See Section \ref{trace} for a definition of the different types of {legs}. \notebyalbert{(by ALBERT) The population of DOWN LEGS in CR-2008 is negligible. These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.}  \notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors. I suggest these changes: cyan$\rightarrow$blue, blue$\rightarrow$red, red$\rightarrow$violet. In this way, blue will be DOWN loops and red will be UP loops, as in previous papers. The same change applies to Figure 4. Also, how about making Figures 3 and 4 a single Figure of four panels? Just an idea.} }
\label{rpoint_demt}
\end{center}
\end{figure}

To compare obtained traced results in both rotations and for each type of lines (associated with differents types of regions), Figure \ref{gradt_demt} shows histograms (normalized to the total amount of the field lines selected) of the temperature radial gradients ($\dr \Tm$). The lack of population around values close to zero is due to the strict condition $|\rho_t| > 0.5$ that discards possible isothermal values, according to DEMT results.

Both rotations are characterized by lines of type 0 with mean values of $-2.5\, \rm MK/\mrsun$, mean values of $2.3\, \rm MK/\mrsun$ in type I and $2.4\, \rm MK/\mrsun$ in type II. The only notable difference is the smaller number of type 0 lines in CR-2208 and the mean value of $4.5\, \rm MK/\mrsun$ in type III for CR-2208 which is twice that for the other rotation.

%\temp{mostrar los gradientes negativos va a ser util en los parrafos posteriores que expliquen porque en las lineas tipo 0 hay valores de $\phi_c$ negativos.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

As an example of the traced magnitudes, Figure \ref{histos_fulldemt} shows the statistical results of both rotations for all field lines types. From top to bottom type 0 to type III. From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$, in each panel the median $m$ is indicated.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} \notebyalbert{The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading. Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.}}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\diego{si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
From the equatorial streamer of both rotations, increasing latitudes show decreasing {coronal base} density, and increasing density scale height and electron temperature. In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of the equatorial streamer. Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres.

A comparison of the results between the two rotations shows that CR-2208 is characterized by lower values (between $11\%\, \rm and\, 16\%$) of coronal base electron density than CR-2082, higher values of density scale height (between $4\%\, \rm and\,19\%$) and higher values of electron temperature (between $6\%\, \rm and\,21\%$).

%To establish if the differences in the results between the two rotations are significant, Section \ref{uncertainties} estimates the error bars due the dominating systematic uncertainties.
%\diego{quizas vale la pena introducir alguna comparacion sobre el campo magnetico, veremos como quedan los comentarios de ceci.}
%{Also, within the streamer belt the magnetic field strength is similar in both rotations in the northern hemisphere, while in the southern hemisphere CR-1915 exhibits $10-80\%$ larger values compared to CR-2081, with increasing difference for larger latitudes. In the coronal holes, the magnetic field strength of CR-1915 is much larger than for CR-2081, exhibiting values up to 50\% larger in the northern hemisphere and more than twice larger in the southern hemisphere.}

\diego{Comienza la energia}\\

%Previous works have found magnetic loops which temperature decrease with height, most generally in equatorial latitudes \citep{huang_2012,nuevo_2013}. This type of loops with negative gradients produce a negative conductive flux that contribute to the heating in the corona. In this work, we compute the loop-integrated energy quantities separately in three different populations of loops.

To compare integrated quantities along loops, we select those close loops where both legs meet the requirements of Section \ref{trace}. In an analogous way to the legs definition, we will refer to them as loops of type 0, I or II.
